---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE)
```

# Download logs from the RStudio CRAN mirror

[![Linux Build Status](https://travis-ci.org/r-hub/cranlogs.svg?branch=master)](https://travis-ci.org/r-hub/cranlogs)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/metacran/cranlogs?svg=true)](https://ci.appveyor.com/project/gaborcsardi/cranlogs)
[![CRAN version](http://www.r-pkg.org/badges/version/cranlogs)](http://www.r-pkg.org/pkg/cranlogs)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/cranlogs)](http://www.r-pkg.org/pkg/cranlogs)

[RStudio](http://www.rstudio.com) publishes the download logs from
their CRAN package mirror daily at http://cran-logs.rstudio.com.

This R package queries a database that contains the daily download
numbers for each package.

The RStudio CRAN mirror is not the only CRAN mirror, but it's a popular one: it's the default choice for RStudio users. The actual number of downloads
 over all CRAN mirrors is unknown.

## Installation

You can install `cranlogs` from CRAN:

```r
install.packages("cranlogs")
```

Or get the development version from Github:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("r-hub/cranlogs")
```

## Usage

It has a very simple API. By default it shows the total number of
package downloads from the last day for which data is available.

```{r}
library(cranlogs)
cran_downloads()
```

The last week (6 days prior to the last day for which data is available), or the last month (29 days prior to the last day for which data is available) can be also easily queried:

```{r}
cran_downloads(when = "last-week")
```

The `package` argument queries a specific package:

```{r}
cran_downloads(when = "last-week", package = c("magrittr", "dplyr"))
```

Alternative intervals can also be specified:

```{r}
cran_downloads(package = "plyr", from = "2014-01-01", to = "2014-02-01")
```

For downloads of R itself, give `"R"` instead of a package:

```{r}
cran_downloads("R")
```

## Top downloaded packages

Last day for which data is available:

```{r}
cran_top_downloads()
```

Last week (6 days prior to the last day for which data is available):

```{r}
cran_top_downloads("last-week")
```

## Raw JSON API

See [here](https://github.com/r-hubs/cranlogs.app).
