
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE)
```

# Download logs from the RStudio CRAN mirror

[![Linux Build Status](https://travis-ci.org/metacran/cranlogs.svg?branch=master)](https://travis-ci.org/metacran/cranlogs)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/metacran/cranlogs?svg=true)](https://ci.appveyor.com/project/gaborcsardi/cranlogs)
[![CRAN version](http://www.r-pkg.org/badges/version/cranlogs)](http://www.r-pkg.org/pkg/cranlogs)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/cranlogs)](http://www.r-pkg.org/pkg/cranlogs)

[RStudio](http://www.rstudio.com) publishes the download logs from
their CRAN package mirror daily at http://cran-logs.rstudio.com.

This R package queries a database that contains the daily download
numbers for each package.

## Installation

You can install `cranlogs` from Github:

```{r eval = FALSE}
library(devtools)
install_github("metacran/cranlogs")
```

## Usage

It has a very simple API. By default it shows the total number of
package downloads from the previous day.

```{r}
library(cranlogs)
cran_downloads()
```

The last week, or the last month can be also easily queried:

```{r}
cran_downloads(when = "last-week")
```

The `package` argument queries a specific package:

```{r}
cran_downloads(when = "last-week", package = c("magrittr", "dplyr"))
```

Alternative intervals can also be specified:

```{r}
cran_downloads(package = "plyr", from = "2014-01-01", to = "2014-02-01")
```

For downloads of R itself, give `"R"` instead of a package:

```{r}
cran_downloads("R")
```

## Top downloaded packages

Last day:

```{r}
cran_top_downloads()
```

Last week:

```{r}
cran_top_downloads("last-week")
```

## Raw JSON API

See [here](https://github.com/metacran/cranlogs.app).
